\chapter{Time Management}

One of the most valuable things that you have is your time. I'll say it again, time is one of your most valuable assets.

Stop squandering this precious resource. Right now. Stop.

Stop what? 

Almost everything you are doing might be a waste of time. 

For example, instead of talking with city hall in getting
bicycle paths swept, an advocate we'll call AA (anonymous
advocate) spent a lot of time sweeping them himself. And to add
uselessness to stupidity, he also spent time cleaning up
graffiti. Finally, AA spent a lot of time complaining that he
"didn't have time" to do everything that needed to be done. 

Really?

That's why we say stop (almost) everything.

Instead of itemizing all the things we should not do, we'll summarize what can be done. 

First of all, if you can delegate anything at all then do it. Now. We'll wait till you get all that junk done by others. 

You should continue doing anything that is critical to maintaining valuable relationships of the organization and yourself. Also, continue doing things that bring in lots of money which is over one hundred dollars per donor. You can let the smaller donors wait a few days. 

If there are things you have committed to and you can't delegate nor get out of them, obviously, you should do them, but duck out as soon as possible. Obviously, you need to attend any meetings you are scheduled for, but try to keep them short this time.

Finally, continue doing those things that are key to your reputatation. For example, many bicycle advocacy organizations have swift public responsese to cyclists deaths. This is a classy and important thing to do. You need to let the victim's family know that you care.

Otherwise, put your phone on mute and let your inbox fill up, for now. Unless that text is from the mayor or city council, you can probably ignore it.

There, now you have time.
